Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-08-08 Ben_Manuscripts/structure_paper/Draft.tex
Draft updates

  \subsubsection{Origin of R-spots}\label{section:rspots}

  In order to more clearly study R-spots, we equilibrated an ordered basin sandwiched 
  configuration at 280K. Obtaining an equilibrium structure at a precise temperature is
  a challenge that force fields often fail to overcome. Wang et al. highlighted the 
  shortcoming of some of the most popular protein force field in predicting the temperature
  dependence of protein structural ensembles \cite{wang_building_2017}. It is possible that   % page 12
  our membrane system, simulated at 300K, does not fully represent the true structure at 300K.
  Lowering the temperature to 280K helped us to better resolve R-spots. 
%  The relative intensity 
%  of R-spots in this system is slightly higher than experiment (1.5 vs. 1.3)

@@

  R-spots originates from the monomer tails.
  %To understand the most likely origin of R-spots, we determined which atoms
  %gave rise to the feature. 
  By removing all non-tail atoms from the trajectory
  and simulating a diffraction pattern with the remaining atoms, we were able to
  isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).

  The tails pack together hexagonally. Since the tails stay nearly flat, we plotted
  their centroids (Figure \ref{fig:centroids}) and measured the angle between
  each centroid and its nearest neighbors with respect to the plane of the
  membrane. We see distinct peaks in the distribution of these angles which are
  consistent with a hexagonally packed configuration
  (Figure~\ref{fig:tail_packing}).

  The peaks in the nearest neighbor angle distribution are consistent with the
  location of R-spots. The peaks of interest in Figure \ref{fig:layered_tails}
  are located at $\pm 33 \degree$ which is the same location where the highest
  intensity of spots are located in the simulated patterns. We confirmed this 
  by radially integrating the 2D WAXS pattern for 
  $\left|\mathbf{q}\right|$ values between 1.4 and 1.57 (between 4
  and 4.5 \AA~in real space). We observe distinct peaks ca. $30
  \degree$, in close agreement with the previously measured angle distribution
  (Figure~\ref{fig:layered_integration}). We performed the same integration on
  the raw experimental data and found the angle at which R-spots reaches its
  highest intensity to be $\pm 37 \degree$ which is a reconcilable difference
  with our simulated results.

@@

  \begin{figure}[!htb]
  \begin{subfigure}{0.32\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rzplot_layered_280K_jet.png}
  	\caption{}\label{fig:sandwiched280K}
  \end{subfigure}
  \begin{subfigure}{0.32\linewidth}
    \includegraphics[width=\textwidth]{tilt_dist.png}
    \caption{}\label{fig:tilt}
  \end{subfigure}
  \begin{subfigure}{0.32\linewidth}
	\centering
	\includegraphics[width=\textwidth]{tails_rzplot_jet.png}
	\caption{}\label{fig:tails_rzplot}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\linewidth}
    \centering
	\includegraphics[width=\textwidth]{centroids_box.png}
  \caption{}\label{fig:centroids}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\linewidth}
        \centering
	        \includegraphics[width=\linewidth]{hexagonal_tail_packing.png}
	        \caption{}~\label{fig:layered_tails}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\textwidth}
        	\centering
	        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
	        \caption{}~\label{fig:layered_integration}
  \end{subfigure}
  \caption{(a) R-spots increases in intensity when the temperature of the system is 
      lowered to 280K. (b) We measured the average angle made between each monomer 
      alkane tail and the membrane plane. The average tilt angle (dashed line) is 
      near -2\degree~which is far from the 37\degree~tilt angle previously used to
      explain R-spots. (c) To isolate the main cause of R-spots, we removed all atoms
      from the trajectory except for carbon atoms that constitute the tails. The
      simulated XRD pattern of the tails-only trajectory still shows R-spots. (d)
      Since the tails stay relatively flat, we plotted the centroid of each tail 
      and observed that they pack hexagonally (for example, green colored centroids
      in the plot surround the red centroid in hexagonal fashion). (e) We hypothesize
      that R-spots is the result of ordered tail packing. Defining
      the membrane plane to be 0\degree, we measured the angles between each alkane 
      chain tail centroid and its nearest neighbor centroids for the equilibrated 
      sandwiched configuration simulated at 280K. Peaks that appear in each distribution
      are centered near $\pm~33\degree$. (f) We radially integrated the simulated XRD
      patterns of the parallel displaced and sandwiched configuration within the region
      bounding R-alkanes. Peaks appear in the same location as the angle distributions
      which corroborates our hypothesis.}~\label{fig:tail_packing}
  \end{figure}

@@

  % BJC8: Is it necessary to focus in on the parallel displaced system for this section? At this
  % point in the story, I haven't shown that it gives rise to R-double. I think the simple systems
  % are conceptually easier to grasp with sandwiched columns. Sliding parallel displaced columns
  % is harder to imagine, and probably not really how the columns are stacked. The parallel displacement
  % is probably less exagerated. 
  % BJC8: that said, if we go with just focusing on parallel displaced, then I can move the R-double section
  % up before this one.
  % MRS9: I think we should start with larger differences rather than smaller, and arguably the greater intensity of R-pi is 
  % a bigger difference.  So it's OK ti put R-double after -- (and it could be that sliding sandwiched columns could still give water h-bonding, since they have carboxyl groups that are on average closer together than sandwiched layered ones).
  %BJC9: keeping above comments for reference

  R-$\pi$ is more intense relative to the experimental system. The difference in intensity
  ranges from 3 times too high in the ordered parallel displaced system to 15 times too 
  high in the ordered sandwiched configuration (Table~\ref{table:relative_inensities_300K}).
%BJC9: keeping below comment for reference  
%MRS9: should be a little more clear why you mean by ``all systems''. In some sense the problem is more that the best explanation might be unaligned columns, which is easier with sandwiched, which are 15 times as much. So here it would make more sense to focus on both types of columns, so you can explain how unaligned (sliding) columns also have a mechanism for reduction. Note that I don't think the columns have to be dynamically sliding (Which would be hard with all the tails entangled) but can be just off-register statically.

  The full width at half maximums (FWHM) of the $q_r$ and $q_z$ cross-sections
  of R-$\pi$ are broader than experiment (Figure~\ref{fig:rpi_exp_comparison}).
  The FWHM of the $q_z$ cross-section is 76 \% larger than experiment and the
  $q_r$ cross-section FWHM is 21\% larger than experiment. Note that the
  experimental data is best fit with a Lorentzian function while the simulated
  patterns are best fit using a Gaussian function. The simulated spectra do not
  incorporate the effects of finite domain sizes, pressure broadening and
  instrumental broadening which would alter the peak shape. In the absence of
  these and other peak broadening effects, the experimental peak would actually
  be narrower, further increasing the discrepancy with simulation.

@@

  We have identified a number of potential ways that simulation conditions,
  forcefield and initial configurations could affect the intensity of R-$\pi$ as
  well as its FWHM in the $q_z$ and $q_r$ directions. We assessed each using a
  simplified model. Our simplified model represents each monomer head group as a
  single point and places them in either a parallel displaced or sandwiched
  configuration. We chose to explore the influence of thermal noise in each
  dimension, the effect of $z$-direction distance correlations between scatterers
  within columns, as well as correlation between columns since these are the
  variables we believe have the largest influence on peak shape and intensity.
  %MRS9: probably best to focus on the variables that we think could cause a problem (i.e. hypotheses to test) first, then talk about how the experiments tested these hypotheses.

  As a baseline, we created a simplified model using the same amount of
  disorder present in our atomistic simulations. There are two sources of
  disorder to consider: thermal motion of atoms and quenched disorder which is
  created by rapid structural rearrangement during early equilibration and is
  largely locked into place for the remainder of the simulation. The latter has
  important implications for the reproducibility of this work since both initial
  configurations and velocity randomization at the beginning of equilibration can
  lead to different quenched configurations. We measured thermal disorder by
  calculating the standard deviation of the distribution of head group center of
  mass positions from their average positions. We measured quenched disorder by
  calculating the standard deviation of the distribution of head group center of
  masses from their idealized average positions. In the $z$-direction, we
  measured the deviation of the head group center of masses from an equally
  spaced column of head groups. In the $xy$ plane, we calculated the deviation in
  radial position from the pore center and the angular deviation from equally
  spaced points surrounding the pore center. The values measured for each system
  and type of disorder are given in Table~\ref{table:quenched_disorder}.

  The intensity of R-$\pi$ can be calculated from a single trajectory of
  uncorrelated configurations rather than from the average of multiple correlated
  trajectories. Theoretically, in order to mimic the simulated system, we should
  build an initial configuration which has the same amount of quenched disorder
  as our simulations and then create a trajectory to which we add thermal
  disorder to the initial configuration in order to create each frame.
  %BJC9 : The following numbers need to be updated: I want to do 40 trajectories with 1000 frames each for both types of trajectories and compare their mean and uncertainty
  The average R-$\pi$ intensity of 40, 100 frame trajectories created in this
  way was 16.0 $\pm$ 4.9. If instead we create a single trajectory from 1000
  initial configurations, the intensity of R-$\pi$ is 16.42, in close agreement
  with the mean of 40 simulations.  We use the latter method for the remainder of
  this work since we can extract the trends we need using a single trajectory at
  a fraction of the computational cost.

  When we simulated the diffraction pattern of a parallel displaced simple
  system trajectory of 1000 independent configurations, each created using the
  parameters for thermal and quenched disorder in order to place points, the
  $q_r$ and $q_z$ profiles of R-$\pi$ are characterized by sharp peaks. We made
  this simple system, and all to follow, 4 times taller in the $z$-direction in
  order to access higher $q_z$ resolution. Figure~\ref{fig:sf_qy_nocorrelation}
  and~\ref{fig:sf_qz_correlation} shows the $q_y$ and $q_z$ cross-sections of
  R-$\pi$ generated by simulating the structure factor of the trajectory. The
  distance between peaks in the $q_y$ cross-section is equivalent to the distance
  between pores in real space.

@@

  The distances between scatterers within each column are correlated with each
  other. In the simplified system described above, we added Gaussian noise to
  the mean positions of an equally spaced column of points. This ignores any
  interaction head groups might have with each other. To remedy this, we drew
  random samples from a multivariate normal distribution defined by the mean
  positions of an equally spaced column of points. We gave the distribution at
  each point along the column the same standard deviation, $\sigma_z$, shown  in
  by Table~\ref{table:quenched_disorder}. We defined a covariance matrix such
  that the covariance, $v$, of the distance, $d$, between scatterers decays
  exponentially from $v$ according to the equation $ve^{-z/L}$, where $L$ is the
  correlation length. Experimentally, the correlation length can be estimated as
  the inverse of the FWHM of the $q_z$ cross-section of R-$\pi$. Accordingly,
  the correlation length of the experimental system is $\geq$ 9 $\AA$. The value
  may be larger since the peak is likely broadened. We simulated the structure
  factor of a simple system built as described above with a correlation length of
  30 $\AA$. We chose 30 $\AA$ in order to exaggerate the effect of correlation
  length for visual purposes. Subsequent structure factor calculations are all
  done with a correlation length of 9 $\AA$. The shape of the $q_y$ cross-section
  (Figure~\ref{fig:sf_qy_correlation}) remains the same while the the $q_z$
  cross-section (Figure~\ref{fig:sf_qz_correlation}) broadens, as seen in
  experiment. Additionally, there is a near 20 \% increase in the maximum
  intensity of R-$\pi$ when the distances between scatterers are correlated.

@@

@@

  Increased thermal noise in the $z$-direction causes a drop in the intensity
  of R-$\pi$, however the $q_r$ profile remains unchanged. When we increase the
  thermal noise in the $z$-direction by 12\% and 27\%, we see a 3 and 15-fold
  decrease in the maximum intensity of R-$\pi$ respectively (Figure
  ~\ref{fig:znoise}). Despite the decrease in intensity, the 3 cross-sections
  have the same shape (Figure~\ref{fig:rpi_xsection_vs_zsigma}, whose sharp
  Bragg-like peaks are not consistent with experiment.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{intensity_vs_zsigma.png}
  \caption{}\label{fig:intensity_vs_zsigma}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{rpi_xsection_vs_zsigma.png}
  \caption{}\label{fig:rpi_xsection_vs_zsigma}
  \end{subfigure}
  \caption{We can decrease the maximum intensity of R-$\pi$ by increasing
  thermal noise in the z-direction, however the $q_r$ cross-section profile does
  not change. (a) The intensity of R-$\pi$ drops precipitously as we increase
  $\sigma_z$. We can decrease the intensity of R-$\pi$, relative to the
  background intensity, as seen in our simulation (blue) by a factor of 3 when we
  increase $\sigma_z$ by 12\% (green) and by a factor of 15 when we increase
  $\sigma_z$ by 27 \% (red). (b) Although the maximum intensity of R-$\pi$
  decreases with increasing $\sigma_z$, the peak shape remains the same.}\label{fig:znoise}
  \end{figure}

  When we allow monomer columns to move independently in the $z$-direction, the
  intensity of R-$\pi$ drops and the $q_r$ cross-section of the simulated
  diffraction patterns smooths out. We created simple systems with varying
  amounts of association between columns. In the low limit, the center of mass
  of columns are situated at the same $z$-coordinate. This is how all simple
  systems have been created up to this point. We allow increasing independence of
  columns by randomly shifting each column in the $z$-direction using a uniform
  distribution bounded by (0, $f \times \mathit{d}_{equil}$) where $f$ ranges
  between 0 and 1. We limit this discussion to the sandwiched configuration since
  it is not feasible for columns in the parallel displaced configuration, as we
  have set them up, to move past each other. The trends seen above apply to both
  the sandwiched and parallel displaced systems. Allowing columns to move
  independently smooths out the $q_r$ cross-section
  (Figure~\ref{fig:column_displacement}). Any amount of dependence results in
  sharp peaks. The intensity of R-$\pi$ decreases with increasing column
  independence. We see an 8-fold decrease in the intensity of R-$\pi$ when $f=1$
  versus when $f=0$. It is likely that the discrepancy between the intensity of 
  R-$\pi$ generated from our simulations versus experiment is due
  to highly correlated columns in our initial configurations.

@@

  We can use what we learned above in order to construct a better model,
  however there will still be shortcomings. We can decrease the intensity of
  R-$\pi$ if we incorporate more $z$-directional noise, which may come from
  increasing the system's temperature. 
  % BJC9: Is there actually a good way to increase thermal noise in the z-direction without
  % temperature? Is decreasing the force constant between bonds viable? 
  We can also decrease the intensity of R-$\pi$, in addition to smoothing the
  $q_y$ cross-section by creating initial configurations whose columns are
  displaced randomly in the $z$-direction. We can achieve better averages if we
  create systems with more pores in the unit cell. In order to make head groups
  stack closer together, we can adjust the parameters for aromatic carbons so
  that head groups stack more closely together. Ultimately, we will need
  extremely long simulation times so that monomers within columns can rearrange
  and sample enough independent configurations to generate a robust simulated XRD
  pattern.

  The architecture of each column is likely in between sandwiched and parallel
  displaced. The parallel displaced configuration that we have simulated in this
  paper is an exaggerated manifestation of the parallel displaced $\pi-\pi$
  stacking mode. The simulated XRD pattern shows faint off-axis features at the
  same $q_r$ value as R-double which is only present in patterns generated from
  parallel displaced configurations. The same feature is present in the
  experimental pattern. The monomers may prefer to be parallel displaced, but
  their displacement is likely only slightly shifted, on the $xy$ plane, from the
  center of mass of their vertically adjacent neighbors. In this way, columns can
  more easily act independently while maintaining a parallel displaced structure.

  % BJC9: Does it still make sense to have this in here? I think we thought that
  % making the system taller might result in a more disordered structure, leading
  % to weaker distance correlations between stacked monomers and a reduced R-pi. 
  % But I've shown that the intensity of R-pi is only weakly dependent on correlation
  % length (20 % difference between correlation length of 0 and 30) and even if there
  % is additional xy noise (for some reason), it will not not decrease R-pi max 
  % intensity. Also, we are getting near the right correlation length (from g(z)
  % and kind of from XRD), which is less than the length of the box. I could
  % just move this to supplemental.   
  The system size in the $z$-direction does not significantly alter the
  intensity of R-$\pi$. We equilibrated a sandwiched system with twice as many
  monomers per column so that the system size doubled in the z-direction. The
  correlation length increases modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA,
  and the intensity of R-$\pi$ decreases from 44.0 to 39.4. Visually, the
  correlation functions are nearly identical (See
  Figure~S-\ref{S-fig:z_correlation_overlay}).

@@

%  \begin{figure}
%  \centering
%  \begin{subfigure}{0.45\textwidth}
%	\centering
%	\includegraphics[width=\textwidth]{layered_yz_correlation.png}
%	\caption{}\label{fig:layered_yz_correlation}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%        \centering
%        \includegraphics[width=\textwidth]{offset_yz_correlation.png}
%        \caption{}\label{fig:offset_yz_correlation}
%  \end{subfigure}
%  %MRS6: have the same color scale in both figures to compare them?
%  \caption{2D pair distribution functions generated from systems built in the 
%	   sandwiched (a) and parallel displaced (b) configurations, provide
%           a more detailed picture of the pore structure in each. The sandwiched
%	   configuration}\label{fig:yz_correlation}
%%MRS6: caption not finished?
%  \end{figure} 
%
%  We plotted the one-dimensional pair distribution function, $g(z)$, for the
%  phenyl rings and for carbon atoms that make up the monomer tails (Figure
%  \ref{fig:zdf}). The plots show clear periodic maxima where layers are present.
%  Layering is most pronounced in the head group region, however there is still a
%  degree of layering that persists into the tail region. Using a Fourier
%  transform on $g(z)$ from the head groups, we see that sandwiched configuration
%  layers stack 4.39 \AA~apart while parallel displaced configuration layers stack
%  4.38 \AA~apart. Both stacking distances are in agreement with those observed
%  in the simulated XRD patterns.
%
%  %MRS6: do you need both the 2D and 1D correlation functions?
%  \begin{figure}
%        \centering
%        \begin{subfigure}{0.45\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{zdf_overlay_layered.png}
%                \caption{}\label{fig:zdf_layered}
%        \end{subfigure}
%        \begin{subfigure}{0.45\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{zdf_overlay_offset.png}
%                \caption{}\label{fig:zdf_offset}
%        \end{subfigure}
%	\caption{We support the existence of layers with the observance of
%		clear periodic maxima in the $z$-direction pair distribution functions of the
%		(a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer, parallel
%		displaced configurations. The extent to which we consider a system to be
%		layered is based on the magnitude of the deviation of the periodic maxima from
%		the average number density. The sandwiched configuration possesses a higher
%		degree of layering than the parallel displaced configuration and, in both
%		cases, the head group region has a higher degree of layer partitioning than the
%		tail region. (See Supporting information for detailed definitions of the head
%		group and tail regions)}\label{fig:zdf}
%  \end{figure}

>>>>

  \subsubsection{The origin of R-spots}\label{section:rspots}

  In order to more clearly study R-spots, we equilibrated an ordered basin sandwiched 
  configuration at 280K. Obtaining an equilibrium structure at a precise temperature is
  a challenge that force fields often fail to overcome. Wang et al. highlighted the 
  shortcoming of some of the most popular protein force field in predicting the temperature
  dependence of protein structural ensembles \cite{wang_building_2017}. It is possible that   % page 12
  our membrane system, simulated at 300K, does not fully represent the true structure at 300K.
  Lowering the temperature to 280K helped us to better resolve R-spots (Figure~\ref{fig:sandwiched280K}). 
%  The relative intensity 
%  of R-spots in this system is slightly higher than experiment (1.5 vs. 1.3)

@@

  %To understand the most likely origin of R-spots, we determined which atoms
  %gave rise to the feature. 
  R-spots originates from the monomer tails. By removing all non-tail atoms from 
  the trajectory and simulating a diffraction pattern with the remaining atoms, 
  we were able to isolate the cause of the spots to the tails 
  (Figure~\ref{fig:tails_rzplot}).

  The tails pack together hexagonally. We plotted the center of mass of the 
  first four tail atoms of each tail originating from each head group 
  (Figure \ref{fig:centroids}). We measured the angle between each center of
  mass and its nearest neighbors with respect to the $xy$ plane of the membrane. 
  We see distinct peaks in the distribution of these angles located ca. 
  $-60\degree$, $0\degree$, and $60\degree$ which is consistent with a 
  hexagonally packed configuration (Figure~\ref{fig:layered_tails}). This 
  ordering dies off at the tail ends, where there is more space to fill 
  causing them to pack nearly isotropically (See supporting information).

  The peaks in the nearest neighbor angle distribution are consistent with the
  location of R-spots. The 2D Fourier transform of a simple hexagonal array 
  constructed based on the peak angles in Figure~\ref{fig:layered_tails}
  shows reflections in the same locations as R-spots, in addition to vertical 
  stacking reflections along the $q_z$ axis that would intersect with R-$\pi$
  (Figure~\ref{fig:hexagonal_ft}).

@@

  \begin{figure}[!htb]
  \begin{subfigure}{0.32\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rzplot_layered_280K_jet.png}
  	\caption{}\label{fig:sandwiched280K}
  \end{subfigure}
  \begin{subfigure}{0.32\linewidth}
    \includegraphics[width=\textwidth]{tilt_dist.png}
    \caption{}\label{fig:tilt}
  \end{subfigure}
  \begin{subfigure}{0.32\linewidth}
	\centering
	\includegraphics[width=\textwidth]{tails_rzplot_jet.png}
	\caption{}\label{fig:tails_rzplot}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\linewidth}
    \centering
	\includegraphics[scale=0.2]{centroids.png}
  \caption{}\label{fig:centroids}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\linewidth}
        \centering
	        \includegraphics[width=\linewidth]{hexagonal_tail_packing.png}
	        \caption{}~\label{fig:layered_tails}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\textwidth}
        	\centering
	        \includegraphics[width=\linewidth]{hexagonal_ft.png}  % generated from hexagonal_packing.py
	        \caption{}~\label{fig:hexagonal_ft}
  \end{subfigure}
  \caption{(a) R-spots increases in intensity when the temperature of the system is 
      lowered to 280K. (b) We measured the average angle made between each monomer 
      alkane tail and the membrane plane. The average tilt angle (dashed line) is 
      near -2\degree~which is far from the 37\degree~tilt angle previously used to
      explain R-spots. (c) To isolate the main cause of R-spots, we removed all atoms
      from the trajectory except for carbon atoms that constitute the tails. The
      simulated XRD pattern of the tails-only trajectory still shows R-spots. (d)
      Since the tails stay relatively flat, we plotted the center of mass of the first
      four carbon atoms of each tail originating from the head groups (for example,
      green colored centroids in the plot surround the red centroid in hexagonal fashion).
      Visually, the packing looks hexagonal. (e) We hypothesize
      that R-spots is the result of ordered tail packing. Defining
      the membrane plane to be 0\degree, we measured the angles between each center of 
      mass and its nearest neighbor center of masses for the equilibrated 
      sandwiched configuration simulated at 280K. Peaks appear in the distribution at 
      $-60\degree$, $0\degree$ and $60\degree$. (f) The Fourier transform of a hexagonally
      packed grid of points defined by the angles in (e) shows intensity at the same
      locations where we expect to see R-spots, as well as intensity along the $q_z$ axis
      where R-$\pi$ would appear.}~\label{fig:tail_packing}
  \end{figure}

@@

  R-$\pi$ is more intense relative to the experimental system. The difference in intensity
  ranges from 3 times too high in the ordered parallel displaced system to 15 times too 
  high in the ordered sandwiched configuration (Table~\ref{table:relative_inensities_300K}).

  % BJC9: This still needs to be worked out. Rest of section should still hold up
  The full width at half maximums (FWHM) of the $q_r$ and $q_z$ cross-sections
  of R-$\pi$ are broader than experiment (Figure~\ref{fig:rpi_exp_comparison}).
  The FWHM of the $q_z$ cross-section is 76 \% larger than experiment and the
  $q_r$ cross-section FWHM is 21\% larger than experiment. Note that the
  experimental data is best fit with a Lorentzian function while the simulated
  patterns are best fit using a Gaussian function. The simulated spectra do not
  incorporate the effects of finite domain sizes, pressure broadening and
  instrumental broadening which would alter the peak shape. In the absence of
  these and other peak broadening effects, the experimental peak would actually
  be narrower, further increasing the discrepancy with simulation.

@@

  We have identified a number of potential ways that simulation conditions,
  forcefield and initial configurations could affect the intensity and shape of
  R-$\pi$. We assessed each using a
  simplified model. Our simplified model represents each monomer head group as a
  single point and places them in either a parallel displaced or sandwiched
  configuration. We chose to explore the influence of thermal noise in each
  dimension, the effect of $z$-direction distance correlations between scatterers
  within columns, as well as correlation between columns since these are the
  variables we believe have the largest influence on peak shape and intensity.
  %MRS9: probably best to focus on the variables that we think could cause a problem (i.e. hypotheses to test) first, then talk about how the experiments tested these hypotheses.

  As a baseline, we created a simplified model using the same amount of
  disorder present in our atomistic simulations. There are two sources of
  disorder to consider: thermal motion of atoms and quenched disorder which is
  created by rapid structural rearrangement during early equilibration and is
  largely locked into place for the remainder of the simulation. The latter has
  important implications for the reproducibility of this work since both initial
  configurations and initial velocity randomization can
  lead to different quenched configurations. We measured thermal disorder by
  calculating the standard deviation of the distribution of head group center of
  mass positions from their average positions. We measured quenched disorder by
  calculating the standard deviation of the distribution of head group center of
  masses from their idealized average positions. In the $z$-direction, we
  measured the deviation of the head group center of masses from an equally
  spaced column of head groups. In the $xy$ plane, we calculated the deviation in
  radial position from the pore center and the angular deviation from equally
  spaced points surrounding the pore center. This method for calculating 
  quenched order inherently includes thermal disorder. The values measured for
  each system and type of disorder are given in Table~\ref{table:quenched_disorder}.

  The intensity of R-$\pi$ can be calculated from a single trajectory of
  uncorrelated configurations rather than from the average of multiple correlated
  trajectories. Theoretically, in order to mimic the simulated system, we should
  build an initial configuration which has the same amount of quenched disorder
  as our simulations and then create a trajectory to which we add thermal
  noise to each subsequent frame. In this scenario, the positions of each scatterer
  will not change in a way that significantly affects the intensity of R-$\pi$
  since most of its character is defined by the far more disordered initial configuration.
  To uncover the expected intensity of R-$\pi$, we would need to average over many
  such trajectories. To bypass this expensive calculation, we instead calculate the
  R-$\pi$ intensity from a trajectory consisting of many independent initial 
  configurations. This simulates the long time scales over which we expect columns
  to sample many configurational states. %We use the latter method for the remainder of
%  this section since we can extract the trends we need using a single trajectory at
%  a fraction of the computational cost.

 %BJC9 : Could show some number like the following
%  The average R-$\pi$ intensity of 40, 100 frame trajectories created in this (1st way mentioned above)
%  way was 16.0 $\pm$ 4.9. If instead we create a single trajectory from 1000
% initial configurations, the intensity of R-$\pi$ is 16.42, in close agreement
%  with the mean of 40 simulations.

  When we simulated the diffraction pattern of a parallel displaced simple
  system trajectory of 1000 independent configurations, the
  $q_r$ and $q_z$ profiles of R-$\pi$ are characterized by sharp peaks. We made
  this simple system, and all to follow, 4 times taller in the $z$-direction in
  order to access higher $q_z$ resolution. Figure~\ref{fig:sf_qy_nocorrelation}
  and~\ref{fig:sf_qz_correlation} shows the $q_y$ and $q_z$ cross-sections of
  R-$\pi$ generated by simulating the structure factor of the trajectory. The
  distance between peaks in the $q_y$ cross-section is equivalent to the distance
  between pores in real space.

@@

  The distances between scatterers within each column are correlated with each
  other. In the simplified system described above, we added Gaussian noise to
  the mean positions of an equally spaced column of points. This ignores any
  interaction head groups might have with each other. To remedy this, we drew
  random samples from a multivariate normal distribution defined by the mean
  positions of an equally spaced column of points. We gave the distribution at
  each point along the column the same standard deviation, $\sigma_z$, shown in
  Table~\ref{table:quenched_disorder}. We defined a covariance matrix such
  that the covariance, $v$, of the distance, $d$, between scatterers decays
  exponentially from $v$ according to the equation $ve^{-d/L}$, where $L$ is the
  correlation length. Experimentally, the correlation length can be estimated as
  the inverse of the FWHM of the $q_z$ cross-section of R-$\pi$. Accordingly,
  the correlation length of the experimental system is $\geq$ 9 $\AA$. The value
  may be larger since the peak is likely broadened. We simulated the structure
  factor of a simple system built as described above with a correlation length of
  30 $\AA$. We chose 30 $\AA$ in order to exaggerate the effect of correlation
  length for visual purposes. Subsequent structure factor calculations are all
  done with a correlation length of 9 $\AA$. The shape of the $q_y$ cross-section
  (Figure~\ref{fig:sf_qy_correlation}) remains the same while the the $q_z$
  cross-section (Figure~\ref{fig:sf_qz_correlation}) broadens, as seen in
  experiment. Additionally, there is a near 20 \% increase in the maximum
  intensity of R-$\pi$ when the distances between scatterers are correlated.

@@

  % BJC9: Got rid of references to R-pi intensity in following paragraph because
  % I can't directly compare R-pi between two simulations starting from different
  % initial configs w/ different velocity randomizations.
  The system size, in the $z$-direction, does not significantly alter $g(z)$. 
  In Figure~\ref{fig:correlation}, oscillations do not fully decay, so a taller
  system may be necessary to fully capture the correlation function. We 
  equilibrated a sandwiched system with twice as many monomers per column 
  so that the system size doubled in the $z$-direction. The correlation length 
  increases modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA. Visually, the
  correlation functions are nearly identical and oscillatory behavior persists
  throughout $g(z)$ in both cases (See Figure~S-\ref{S-fig:z_correlation_overlay}).

@@

  Increased thermal noise in the $z$-direction causes a drop in the intensity
  of R-$\pi$, however the $q_r$ profile remains unchanged. When we increase the
  thermal noise of our parallel displaced simple system in the $z$-direction by
  12\% and 27\%, we see a 3 and 15-fold decrease in the maximum intensity of 
  R-$\pi$ respectively (Figure~\ref{fig:znoise}). Despite the decrease in 
  intensity, the 3 cross-sections have the same shape 
  (Figure~\ref{fig:rpi_xsection_vs_zsigma}, whose sharp Bragg-like peaks are
  not consistent with experiment.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{intensity_vs_zsigma.png}
  \caption{}\label{fig:intensity_vs_zsigma}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{rpi_xsection_vs_zsigma.png}
  \caption{}\label{fig:rpi_xsection_vs_zsigma}
  \end{subfigure}
  \caption{We can decrease the maximum intensity of R-$\pi$ by increasing
  thermal noise in the $z$-direction, however the $q_r$ cross-section profile does
  not change. (a) The intensity of R-$\pi$ drops precipitously as we increase
  $\sigma_z$. We can decrease the intensity of R-$\pi$, relative to the
  background intensity, as seen in our simulation (blue) by a factor of 3 when we
  increase $\sigma_z$ by 12\% (green) and by a factor of 15 when we increase
  $\sigma_z$ by 27 \% (red). (b) Although the maximum intensity of R-$\pi$
  decreases with increasing $\sigma_z$, the peak shape remains the same.}\label{fig:znoise}
  \end{figure}

  When we allow monomer columns to move independently in the $z$-direction, the
  intensity of R-$\pi$ drops and the $q_r$ cross-section of the simulated
  diffraction patterns smooths out. We created simple systems with varying
  amounts of association between columns. In the low limit, the center of mass
  of columns are situated at the same $z$-coordinate. This is how all simple
  systems have been created up to this point. We allow increasing independence of
  columns by randomly shifting each column in the $z$-direction according to a uniform
  distribution bounded by (0, $f \times \mathit{d}_{equil}$) where $f$ ranges
  between 0 and 1. We limit this discussion to the sandwiched configuration since
  it is not feasible for columns in the parallel displaced configuration, as we
  have set them up, to move past each other. The trends seen above apply to both
  the sandwiched and parallel displaced systems. 
  %BJC9: ^need to prove that in supplemental?  
  Allowing columns to move
  independently smooths out the $q_r$ cross-section
  (Figure~\ref{fig:column_displacement}). Any amount of dependence results in
  sharp peaks. The intensity of R-$\pi$ decreases with increasing column
  independence. We see an 8-fold decrease in the intensity of R-$\pi$ when $f=1$
  versus when $f=0$. It is likely that the discrepancy between the intensity of 
  R-$\pi$ generated from our simulations versus experiment is primarily due
  to highly correlated columns in our initial configurations.

@@

  The architecture of each column is likely in between sandwiched and parallel
  displaced. The parallel displaced configuration that we have simulated in this
  paper is an exaggerated manifestation of the parallel displaced $\pi-\pi$
  stacking mode. The experimental WAXS pattern shows faint off-axis features at the
  same $q_r$ value as R-double which is only present in simulated patterns generated from
  parallel displaced configurations. The monomers may prefer to be parallel displaced, but
  their displacement is likely only slightly shifted, on the $xy$ plane, from the
  center of mass of their vertically adjacent neighbors. In this way, columns can
  more easily act independently while maintaining a parallel displaced structure.

  We can use what we learned above in order to construct a better model,
  however there will still be shortcomings. We can decrease the intensity of
  R-$\pi$ if we incorporate more $z$-directional noise, which may come from
  increasing the system's temperature. 
  % BJC9: Is there actually a good way to increase thermal noise in the z-direction without
  % temperature? Is decreasing the force constant between bonds viable? 
  We can also decrease the intensity of R-$\pi$, in addition to smoothing the
  $q_y$ cross-section by creating initial configurations whose columns are
  displaced randomly in the $z$-direction. We can achieve better averages if we
  create systems with more pores in the unit cell. In order to make head groups
  stack closer together, we can adjust the force field parameters for aromatic 
  carbons. Ultimately, we will need extremely long simulation times, or enhanced
  sampling techniques so that monomers within columns can rearrange and sample
  enough independent configurations to generate a robust simulated XRD pattern.

@@
